Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

\subsection{vgg19 model}
For the vgg19 model that most neural style transfer implementations available are based on,
The inputs and outpus of each layer are all arrays with 4 dimensions.
The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
for example ``$3$-dimension vector''. 
Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.
We give an illustration for the vgg19 model in Figure \ref{vgg512}
\begin{figure}
\center
\includegraphics[width=\textwidth]{vgg512.pdf}
\caption{The VGG19 model with an $512\times512$ RGB image as its input \label{vgg512}}
\end{figure}

@@

The content loss is the easier one of the two losses.

>>>>

\subsection{vgg19 model}
For the vgg19 model that most neural style transfer implementations available are based on,
The inputs and outpus of each function are all arrays with 4 dimensions.
The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
for example ``$3$-dimension vector''. 
Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.
We give an illustration for the vgg19 model in Figure \ref{vgg512}
\begin{figure}
\center
\includegraphics[width=\textwidth]{vgg512.pdf}
\caption{The VGG19 model with an $512\times512$ RGB image as its input \label{vgg512}}
\end{figure}

@@

The content loss is the easier one to explain of the two losses.
It is the mean square error between the outputs of a certain function in the
vgg19 taking the current argument image and the content image as inputs respectively.
We say ``a certain'' function because the output of which function to choose is
adjustable.
A typical choice is the output of \verb|conv_4| function. See Figure \ref{contentloss}.
\begin{figure}
\center
\includegraphics[width=\textwidth]{contentloss.pdf}
\caption{The content loss \label{contentloss}}
\end{figure}
